Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-03 p2/ordering.tex
Clarifications

\begin{mylem}\mlabel{equiv_simple_same_commands}
If two simple sequences $A$ and $B$ are equivalent
and do not break all filesystems ($A\equiv \wrksx{B}$),
then they must contain the same commands.
\end{mylem}
\begin{proof}
% BACK_TO_THE_FS
% TODO Rule?
Let $A$ and $B$ be simple sequences
such that $A\equiv \wrksx{B}$,
and $\FS$ be a filesystem that they are defined on.

We use a proof by contradiction, and assume that they do not contain the same commands.
Without loss of generality, we can assume
that $A$
contains $\cxynv$, and $B$ either contains a different command
$\czwnv$ on $n$, or no command on $n$ at all.
As $A$ is simple, we know that $\cxynv$ is not an assertion command,
and therefore $[x]\neq [y]$ and $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
$A$ and $B$ cannot be equivalent.
Otherwise we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
and that $w=y$ as $B\aFS(n)$ must
be $y$ and $B$ only has one command on $n$.
However, then $\czwnv=\cxynv$, which is a contradiction.
\end{proof}

@@

\begin{mylem}\mlabel{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = \{T \whr T\equiv S \:\wedge\: T \mbox{~is simple} \}. \]
\end{mylem}

\begin{proof}
First, we prove, by contradiction, that if a simple sequence $T$, $T\equiv S$, then $T\in\orderset{S}$.
We use an inverse proof and assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv \wrksx{S}$.

@@

\begin{mydef}[$\ordsign$]
It follows from \cref{simple_reorder_equiv} that given a simple set of commands $S$,
which can be applied to a filesystem in some order without breaking it,
this order will be in $\orderset{S}$,
and all sequences in $\orderset{S}$
represent the same partial endofunction on filesystems.
This allows us to treat such a set as a sequence for any purpose
where the internal order of the commands is irrelevant.
We write $\ordp{S}$ to represent this endofunction.
We leave $\ordp{S}$ undefined if such an order does not exist.
\end{mydef}

>>>>

\begin{mylem}\mlabel{equiv_simple_same_commands}
If two simple sequences $A$ and $B$ are equivalent
and do not break all filesystems ($A\equiv \wrksx{B}$),
then they must contain the same commands.
\end{mylem}
\begin{proof}
% BACK_TO_THE_FS
% TODO Rule?
Let $A$ and $B$ be simple sequences
such that $A\equiv \wrksx{B}$,
and $\FS$ be a filesystem that they are defined on.
We use a proof by contradiction, and assume that they do not contain the same commands.
Without loss of generality, we can assume
that $A$
contains $\cxynv$, and $B$ either contains a different command
$\czwnv$ on $n$, or no command on $n$ at all.
As $A$ is simple, we know that $\cxynv$ is not an assertion command,
and therefore either $[x]\neq [y]$, or it is a replacement command.

If $[x]\neq [y]$, then $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
Therefore, if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)\neq y=A\aFS(n)$ and
$A$ and $B$ cannot be equivalent.
If $B$ includes $\czwnv$, then we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
and that $w=y$ as $B\aFS(n)$ must
be $y$ and $B$ only has one command on $n$.
This means that $\czwnv=\cxynv$, which is a contradiction.

If $\cxynv$ is a replacement command, then we know $[x]=[y]=[\valfx]$, and
$[\FS(n)]=[\valfx]$. If $\FS(n)=y$, then instead of this filesystem,
consider $\fsreplacement{\FS}{n}{\valf}$ where $\valf$ is any file value
other than $y$.
(We assume that there are more than one file values; if this is not so,
$\cffa{n}$ becomes an assertion command.)
From here the proof concludes in the same way as above.
\end{proof}

@@

\begin{mylem}\mlabel{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$.
% that is, \[ \orderset{S} = \{T \whr T\equiv S \:\wedge\: T \mbox{~is simple} \}. \]
\end{mylem}

\begin{proof}
First, we prove, by contradiction, that if $T$ is a simple sequence and $T\equiv S$, then $T\in\orderset{S}$.
We use an inverse proof and assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv \wrksx{S}$.

@@

It follows from \cref{simple_reorder_equiv} that given a simple set of commands $S$,
which can be applied to a filesystem in some order without breaking it,
this order will be in $\orderset{S}$,
and all sequences in $\orderset{S}$
represent the same partial endofunction on filesystems.
This allows us to treat such a set as a sequence for any purpose
where the internal order of the commands is irrelevant.
\begin{mydef}[$\ordp{S}$]
For a simple set or sequence of commands $S$,
$\ordp{S}$ is the unique partial endofunction on filesystems
defined by any order in $\orderset{S}$.
We leave $\ordp{S}$ undefined if such an order does not exist.
\end{mydef}
